Modeling the Latent Space of Symbolic String Quartet Music

### 2021-06-07 papers/final/alex/paper.tex
add gdrive link to paper

MusicVAE, part of the Magenta project, is a variational Long
Short-Term Memory (LSTM) autoencoder for MIDI that incorporates a
novel hierarchical structure using a ``conductor'' recurrent layer in
its decoder model to better capture structure at multiple levels and
avoid the problem of ``posterior/mode collapse'' whereby a generative
model learns to ignore its latent codes and rely on autoregression to
generate output sequences \cite{roberts_hierarchical_2018}. This model
is trained on 16-bar paragraphs of music and is capable of generating
new melodies that blend two given melodies together via latent space
interpolation. Among the literature surveyed, MusicVAE's approach is
the most similar to this work; in comparison our model is
significantly simpler and works on a single bar of music at a time.

@@

A website with several samples of the original input MIDI tracks, the
autoencoded outputs, and interpolations, is presented at: \textbf{TODO}

>>>>

MusicVAE, part of the Magenta project, is a variational Long
Short-Term Memory (LSTM) autoencoder for MIDI that incorporates a
novel hierarchical structure using a ``conductor'' recurrent layer in
its decoder model to better capture structure at multiple levels and
avoid the problem of ``posterior/mode collapse'' whereby a generative
model learns to ignore its latent codes and rely on autoregression to
generate output sequences \cite{roberts_hierarchical_2018}. This model
is trained on 16-bar paragraphs of music and is capable of generating
new melodies that blend two given melodies together via latent space
interpolation. Among the literature surveyed, MusicVAE's approach is
the most similar to this work; in comparison MusicVAE dedicates
significant effort to devising an architecture that allows the model
to generate very long sequences of notes, which is beneficial for
other generation tasks but not strictly necessary for
interpolation. Our model is significantly simpler and demonstrates
that interpolation works well even on a single bar of music at a time.

@@

A collection of several samples of the autoencoded outputs and
interpolations, is presented at:
\href{https://drive.google.com/drive/folders/12o04uubXtP8WdI62Xe5fjE6wQgzCPG8n?usp=sharing
  (Google Drive link)}
